Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-10-22 paperDraft3.tex
started edits

\subsubsection{Model Structure}
In the first phase of testing, we assume the vehicle miles at failure, $y$,
follow a lifetime distribution with an unknown set of parameters that include
a rate parameter $\lambda_{ij}$.
Introducing notation,
\begin{equation}
y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
j=1,2,...,s \quad k=1,2,...,n_{ij}
\end{equation}
where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$,
$v$ is the number of vehicles, $s$ is the number of failure modes, and $n_{ij}$
are the number of failures of vehicle $i$ failure mode $j$. The number of
failure modes is assumed fixed and known \textit{a priori}.

@@

One normal assumption used in reliability growth modeling is nondecreasing
failure rates; that is either the fixes were effective or had no effect, but did
not degrade the family of vehicles.  This should generally be the case, but
because we are dealing with complex systems and testing conditions are rarely
completely consistent, we will sometimes see decreases in failure rates after
adjustments are made.  Therefore for the Phase 2 data, we write the rate
parameters as a function of the rate parameters found in Phase 1. In particular,
we define $\lambda_{ij}^{P2}=(\rho_{j})\lambda_{ij}^{P1}$ where $\rho_{j}$
represents the between phase change in failure mode $j$. Given this definition
of $\lambda_{ij}^{P2}$, we again model the miles to failure for a given vehicle
and failure mode using the same lifetime distribution from Test Phase 1.  We
will choose a prior distribution for the parameter $\rho_{j}$ that has positive
support.  If $\rho_{j}$ is less than one, this represents an improvement in
reliability.  After Phase 2 we can look again at failure rates across failure
modes and vehicles and obtain an overall estimate of the rate for the family of
vehicles.  The analysis of Test Phase 3 follows the same pattern as that shown
in Phase 2. At the end of Phase 3, we can look at failure rates across failure
modes and vehicles and obtain an overall estimate of the rate for the family of
vehicles. Future tests will be planned based on the inferences of Phase 3.

@@

First the exponential model, Test Phase 1,
\begin{equation} f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}
y_{ijk})
\end{equation}
Test Phase 2,
\begin{equation}
f(y_{ijk}|\lambda_{ij}\rho_{1,j})=\lambda_{ij}\rho_{1,j}
\exp(-\lambda_{ij}\rho_{1,j} y_{ijk})
\end{equation}
Test Phase 3,
\begin{equation}
f(y_{ijk}|\lambda_{ij}\rho_{1,j}\rho_{2,j})=\lambda_{ij}\rho_{1,j}\rho_{2,j}
\exp(-\lambda_{ij}\rho_{1,j}\rho_{2,j} y_{ijk})
\end{equation}

@@

\begin{figure}
  \centering
      \includegraphics[width=8cm, height=6cm]{Boxplots}
  \caption{Comparing EMTF for Different Models}
\end{figure}

The plots show that the posterior distributions from the Weibull model have a
good amount more spread than the exponential.  This is somewhat expected given
the Weibull model is estimating two model parameters to the exponentials one,
but what is concerning is that the center of the distributions is also quite
different between the two models.  All of the Weibull EMTF posterior means
are higher than the exponentials.  This is the first sign that the exponential
model may not be a good fit to the data.

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Rplot1}
  \caption{Plot 1}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Rplot2}
  \caption{Plot 2}
  \label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots}
\label{fig:test}
\end{figure}

@@

For a test that fails, the \emph{posterior producer's risk} is the probability
that $\pi \geq \pi_{0}$, or $P \text{(}\pi \ge \pi_0 \vert \text{Test Is
Failed)}$. Notice that this is simply the posterior probability that $\pi \ge
\pi_0$ given that we have observed more than $c$ failures. In the exponential
case, if we let $\pi$ be the system failure rate $\lambda_S$, then using Bayes'
Theorem, and assuming a maximum allowable posterior producer's risk $\alpha$, an
expression for the posterior producer's risk for the exponential test plan
$(T,c)$ is
$$
\begin{aligned}
    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{\lambda_0}^{\infty}
    \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S)
    d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} [ \sum_{W=0}^c
    \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
    {\int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
\end{aligned}
$$
\\
\\
For simplicity we if fix c to be zero and then perform Monte Carlo integration
using N posterior draws $ \lambda_S^{(j)} $
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &=
	 \frac{\int_{\lambda_0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
	 {\int_{0}^{\infty} exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
	 \frac{\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
	 \lambda_0)} {\sum_{j = 1}^{N} exp(-\lambda_S^{(j)} T)} \end{aligned}
$$

@@

$$
\begin{aligned}
    P(\lambda_S \leq \lambda_1 \; \vert \; \text{Test Is Passed)} &= P(\lambda_S
    \leq \lambda_1 \; \vert \; W \leq c) \\ &= \int_{0}^{\lambda_1} p(\lambda_S \;
    \vert W > c) d\lambda_S \\ &= \int_{0}^{\lambda_1} \frac{f(W > c \vert
    \lambda_S)}{\int_{0}{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\ &=
    \frac{\int_{0}^{\lambda_1} [ \sum_{W=0}^c \frac{(\lambda_S T)^W
    exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [
    \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \beta
\end{aligned}
$$
\\
\\
For simplicity we if fix c to be zero and then perform Monte Carlo integration
using N posterior draws $ \lambda_S^{(j)} $ $$
\begin{aligned}
	 P(\lambda_S \leq \lambda_1 \; \vert \; W = 0) &= \frac{\int_{0}^{\lambda_1}
	 exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S
	 T)p(\lambda_S)d\lambda_S} \\ &\approx \frac{\sum_{j = 1}^{N}
	 exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \leq \lambda_1)} {\sum_{j = 1}^{N}
	 exp(-\lambda_S^{(j)} T)}
\end{aligned}
$$

\subsubsection{Weibull Case}
In the exponential case, we defined our quantity of interest that is related to
system reliability at a given time $\pi$ to be equal to the system failure rate
$\lambda_S$.  This distributional assumption gave us a convenient distributional
form for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
When we assume the miles to failure for each system component follows a Weibull
distribution the system failure counts no longer follow a homogeneous Poisson
process.  Because each component failure rate now varies with time each
component failure count follows a non-homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\gamma_i \lambda_i t^{\gamma_i})$.  In this case we no longer
have a closed form for the system failure rate $\lambda_S$.  The exception being
if we can assume a single shape parameter $\gamma$ for all components.  In this
case, it can be shown [A1] that the system failure count follows a non-homogeneous
Poisson process $W(t) \sim \text{Poisson}(\gamma \lambda_S t^{\gamma})$.  Now,
we can use the same approach as with the exponential distribution. An expression
for the posterior producer's risk for the exponential test plan $(T,c)$ is
$$
\begin{aligned}
    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{0}^{\infty}
    \int_{\lambda_0}^{\infty} \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty}
    \int_{0}^{\infty} f(W > c \vert \lambda_S) d\lambda_S d\gamma} d\lambda_S
    d\gamma \\ &= \frac{\int_{0}^{\infty} \int_{\lambda_0}^{\infty}
    [\sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W exp(-\gamma \lambda_S
    T^{\gamma})}{W!}]p(\lambda_S)p(\gamma)d\lambda_S d\gamma} {\int_{0}^{\infty}
    \int_{0}^{\infty} [ \sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W
    exp(-\gamma \lambda_S T^{\gamma})} {W!}]p(\lambda_S) p(\gamma)
    d\lambda_Sd\gamma} \leq \alpha
\end{aligned}
$$
\\
\\
Once again we can simplify by setting c to be zero and then perform Monte Carlo
integration using N posterior draws for both $\lambda_S^{(j)}$ and
$\gamma^{(j)}$
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{0}^{\infty}
	 \int_{\lambda_0}^{\infty} exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} exp(-
	 \gamma \lambda_S T^{\gamma})p(\lambda_S) p(\gamma) d\lambda_S d\gamma} \\
	 &\approx \frac{\sum_{j = 1}^{N} exp(-\gamma^{(j)} \lambda_S^{(j)}
	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N}
	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})} \end{aligned}
$$

@@

It should be noted that if $\pi_0$, $\pi_1$, $\alpha$ and $\beta$ are set to
unrealisitc values there can be situations where no combinations of failures
allowed and test miles required will satisfy these probability statements.  In
this paper we have focused on test plans for single units, but this methodology
can be extended to find test plans that allow for a changing number of testing
units.  In this case you would find combinations of failures allowed and test
miles required and number of vehicles tested that satisfy the risk requirements.
More details and examples of this can be found in the assurance testing section
of Hamada et al. ~\cite{ref4}

@@

>>>>

\subsubsection{Model Structure}
Introducing notation, for each phase of testing we have failure time data for a
given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the end of that
testing phase. In the first phase of testing, we assume the vehicle miles
between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a lifetime
distribution with an unknown set of parameters that include a rate parameter
$\lambda_{ij}$.
\begin{equation}
y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
j=1,2,...,s \quad k=1,2,...,n_{ij}
\end{equation}
where $v$ is the number of vehicles, $s$ is the number of failure modes, and
$n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$. The number
of failure modes is assumed fixed and known \textit{a priori}.

@@

% This section needs a little work to make it more clear about the different
% phases having the same lambda.  The notation should work together with the
% distribution section after it.
One normal assumption used in reliability growth modeling is nondecreasing
failure rates; that is either the fixes were effective or had no effect, but did
not degrade the family of vehicles.  This should generally be the case, but
because we are dealing with complex systems and testing conditions are rarely
completely consistent, we will sometimes see decreases in failure rates after
adjustments are made.  Therefore for the Phase 2 data, we write the rate
parameters as a function of the rate parameters found in Phase 1. In particular,
we define $\lambda_{ij}=(\rho_{j}^{P2})\lambda_{ij}$ where $\rho_{j}^{P2}$
represents the between phase change in failure mode $j$. Given this definition
of of the rate parameter, we again model the miles to failure for a given
vehicle and failure mode using the same lifetime distribution from Test Phase 1.
We will choose a prior distribution for the parameter $\rho_{j}^{P2}$ that has
positive support.  If $\rho_{j}^{P2}$ is less than one, this represents an
improvement in reliability.  After Phase 2 we can look again at failure rates
across failure modes and vehicles and obtain an overall estimate of the rate for
the family of vehicles.  The analysis of Test Phase 3 failure rate
$\lambda_{ij}=(\rho_{j}^{P3})\rho_{j}^{P2}\lambda_{ij}$, following the same
pattern as that shown in Phase 2. At the end of Phase 3, we can look at failure
rates across failure modes and vehicles and obtain an overall estimate of the
rate for the family of vehicles. Future tests will be planned based on the
inferences of Phase 3.

@@

First the exponential model, Test Phase 1,
\begin{equation} f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}
y_{ijk})
\end{equation}
Test Phase 2,
\begin{equation}
f(y_{ijk}|\lambda_{ij}\rho_{1,j})=\lambda_{ij}\rho_{j}^{P2}
\exp(-\lambda_{ij}\rho_{j}^{P2} y_{ijk})
\end{equation}
Test Phase 3,
\begin{equation}
f(y_{ijk}|\lambda_{ij}\rho_{j}^{P3}\rho_{j}^{P2})=\lambda_{ij}\rho_{1,j}\rho_{2,j}
\exp(-\lambda_{ij}\rho_{j}^{P3}\rho_{j}^{P2} y_{ijk})
\end{equation}

@@

% going to add a table that will have the posterior means and 90% credible
% interval limits
\begin{figure}
  \centering
      \includegraphics[width=8cm, height=6cm]{Boxplots}
  \caption{Comparing EMTF for Different Models}
\end{figure}

Figure 1 show that the posterior distributions from the Weibull model have a
good amount more spread than the exponential.  This is somewhat expected given
the Weibull model is estimating two model parameters to the exponentials one,
but what is concerning is that the center of the distributions is also quite
different between the two models.  All of the Weibull EMTF posterior means
are higher than the exponentials.  This is the first sign that the exponential
model may not be a good fit to the data.

@@

% these plots will be redone and I plan to add a contrasting version of them
% using the exponential model
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Rplot1}
  \caption{Plot 1}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Rplot2}
  \caption{Plot 2}
  \label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots}
\label{fig:test}
\end{figure}

@@

For a test that fails, the \emph{posterior producer's risk} is the probability
that $\pi \geq \pi_{0}$, or $P \text{(}\pi \ge \pi_0 \vert \text{Test Is
Failed)}$. Notice that this is simply the posterior probability that $\pi \ge
\pi_0$ given that we have observed more than $c$ failures. In the exponential
case, if we let $\pi$ be the system failure rate $\lambda_S$, then using Bayes'
Theorem, and assuming a maximum allowable posterior producer's risk $\alpha$, an
expression for the posterior producer's risk for the exponential test plan
$(T,c)$ is
$$
\begin{aligned}
    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{\lambda_0}^{\infty}
    \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S)
    d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} 1 - [ \sum_{W=0}^c
    \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
    {\int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
\end{aligned}
$$
\\
\\
For simplicity we if fix c to be zero and then perform Monte Carlo integration
using N posterior draws $ \lambda_S^{(j)} $
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &=
	 \frac{\int_{\lambda_0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
	 {\int_{0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
	 \frac{\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
	 \lambda_0)} {\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)} \end{aligned}
$$

@@

$$
\begin{aligned}
    P(\lambda_S \leq \lambda_1 \; \vert \; \text{Test Is Passed)} &= P(\lambda_S
    \leq \lambda_1 \; \vert \; W \leq c) \\ &= \int_{0}^{\lambda_1} p(\lambda_S \;
    \vert W > c) d\lambda_S \\ &= \int_{0}^{\lambda_1} \frac{f(W > c \vert
    \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S) d\lambda_S} d\lambda_S \\ &=
    \frac{\int_{0}^{\lambda_1} [ \sum_{W=0}^c \frac{(\lambda_S T)^W
    exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} [
    \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \beta
\end{aligned}
$$
\\
\\
For simplicity we if fix c to be zero and then perform Monte Carlo integration
using N posterior draws $ \lambda_S^{(j)} $ $$
\begin{aligned}
	 P(\lambda_S \leq \lambda_1 \; \vert \; W = 0) &= \frac{\int_{0}^{\lambda_1}
	 exp(-\lambda_S T)p(\lambda_S)d\lambda_S} {\int_{0}^{\infty} exp(-\lambda_S
	 T)p(\lambda_S)d\lambda_S} \\ &\approx \frac{\sum_{j = 1}^{N}
	 exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \leq \lambda_1)} {\sum_{j = 1}^{N}
	 exp(-\lambda_S^{(j)} T)}
\end{aligned}
$$

\subsubsection{Weibull Case}
In the exponential case, we defined our quantity of interest that is related to
system reliability at a given time $\pi$ to be equal to the system failure rate
$\lambda_S$.  This distributional assumption gave us a convenient distributional
form for our system failure counts with $W(t) \sim \text{Poisson}(\lambda_S t)$
When we assume the miles to failure for each system component follows a Weibull
distribution the system failure counts no longer follow a homogeneous Poisson
process.  Because each component failure rate now varies with time each
component failure count follows a non-homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\gamma_i \lambda_i t^{\gamma_i})$.  In this case we no longer
have a closed form for the system failure rate $\lambda_S$.  The exception being
if we can assume a single shape parameter $\gamma$ for all components.  In this
case, it can be shown [A1] that the system failure count follows a non-homogeneous
Poisson process $W(t) \sim \text{Poisson}(\gamma \lambda_S t^{\gamma})$.  Now,
we can use the same approach as with the exponential distribution. An expression
for the posterior producer's risk for the exponential test plan $(T,c)$ is
$$
\begin{aligned}
    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{0}^{\infty}
    \int_{\lambda_0}^{\infty} \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty}
    \int_{0}^{\infty} f(W > c \vert \lambda_S) d\lambda_S d\gamma} d\lambda_S
    d\gamma \\ &= \frac{\int_{0}^{\infty} \int_{\lambda_0}^{\infty} 1 -
    [\sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W exp(-\gamma \lambda_S
    T^{\gamma})}{W!}]p(\lambda_S)p(\gamma)d\lambda_S d\gamma} {\int_{0}^{\infty}
    \int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\gamma \lambda_S T^{\gamma})^W
    exp(-\gamma \lambda_S T^{\gamma})} {W!}]p(\lambda_S) p(\gamma)
    d\lambda_Sd\gamma} \leq \alpha
\end{aligned}
$$
\\
\\
Once again we can simplify by setting c to be zero and then perform Monte Carlo
integration using N posterior draws for both $\lambda_S^{(j)}$ and
$\gamma^{(j)}$
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &= \frac{\int_{0}^{\infty}
	 \int_{\lambda_0}^{\infty} 1 - exp(- \gamma \lambda_S T^{\gamma})p(\lambda_S)
	 p(\gamma) d\lambda_S d\gamma} {\int_{0}^{\infty} \int_{0}^{\infty} 1 - exp(-
	 \gamma \lambda_S T^{\gamma})p(\lambda_S) p(\gamma) d\lambda_S d\gamma} \\
	 &\approx \frac{\sum_{j = 1}^{N} 1 - exp(-\gamma^{(j)} \lambda_S^{(j)}
	 T^{\gamma^{(j)}}) I(\lambda_S^{(j)} \geq \lambda_0)} {\sum_{j = 1}^{N} 1 -
	 exp(- \gamma^{(j)} \lambda_S^{(j)} T^{\gamma^{(j)}})} \end{aligned}
$$

@@

% This part should be expanded quite a bit and will extend into the discussion
% section.
It should be noted that if $\pi_0$, $\pi_1$, $\alpha$ and $\beta$ are set to
unrealisitc values there can be situations where no combinations of failures
allowed and test miles required will satisfy these probability statements.  In
this paper we have focused on test plans for single units, but this methodology
can be extended to find test plans that allow for a changing number of testing
units.  In this case you would find combinations of failures allowed and test
miles required and number of vehicles tested that satisfy the risk requirements.
More details and examples of this can be found in the assurance testing section
of Hamada et al. ~\cite{ref4}

@@

\subsection{Notes}
Need to say somewhere we are assuming "bad-a-old" for the Weibull model.
